### 2019-03-07 experiments.tex
parallel sorts now

>>>>

Running TSTL's random tester without checking for determinism, we can
see that both sorting algorithms always produce sorted output.  If we run with {\tt --checkDeterminism --determinismDelay 0}, however, a
test case showing the {\tt swapsort} behaving nondeterministically is
almost instantly produced (it takes less than 3 seconds).  If we comment out the call to {\tt
  swap\_sort\_parallel} and only check the parallel merge sort, however, TSTL
finds no nondeterministic behavior.  Running tests of the merge sort
with nondeterminism detection turned on results in a slowdown of approximately
40\%.

Reducing a lengthy test showing nondeterminism of the swapsort to a
short test case using delta-debugging usually takes less than two
minutes.  If the number of attempts to produce nondeterminism is
increased in the reducer using the {\tt --determinismTries 10} option,
the resulting test will be usually be very compact, e.g.:

{\scriptsize
\begin{code}
data0 = []    
val0 = 3      
val1 = -9    
data0.append((val0,val1)) 
val2 = -1                         
data0.append((val1,val2))
data0.append((val1,val1))  
sorted0 = swapsort.swap\_sort\_parallel(data0)      
\end{code}
}

For this simple example, more sophisticated delta-debugging strategies
are not needed; we only want to see the code behaving
nondeterministically, and do not care about preserving a higher probability of nondeterminism.

### 2019-03-07 introduction.tex
value pool formalism, parallel sort example
parallel sorts now

This paper proposes (1) a number of formal definitions of types of
nondeterminism (\emph{horizontal} and \emph{vertical}) and (2) an implementation, based on these definitions, for detecting and debugging
nondeterminism in property-based testing.  The implementation is based
on an approach where (3) horizontal determinism is considered as a
kind of \emph{reflexive differential testing} and (4) vertical
determinism is specialized to the common case of \emph{failure determinsim}.
We further propose modifications to the widely used delta-debugging algorithm in order to better handle
nondeterminism as a test property.

@@

We use a set
of case studies of real-world, widely-used, Python libraries to demonstrate the
utility of our ideas.  Failure determinism directly
produces a more than 5\% improvement in mutation score for an already highly
effective automated test generation tool for a file system, with no
additional specification or test design burden.

>>>>

This paper proposes (1) a number of formal definitions of types of
nondeterminism (\emph{horizontal} and \emph{vertical}) (see Section \ref{sec:formal}) and (2) an implementation, based on these definitions, for detecting and debugging
nondeterminism in property-based testing.  The implementation is based
on an approach where (3) horizontal determinism is considered as a
kind of \emph{reflexive differential testing} (4) vertical
determinism is specialized to the common case of \emph{failure
  determinism}, and (5)  in both cases the formalism is made practical
by using the \emph{value pool} model of unit tests to define a useful
granularity for nondeterminism detection (see Section \ref{sec:pools}).
We further propose modifications to the widely used delta-debugging algorithm in order to better handle
nondeterminism as a test property.

@@

We use a set
of case studies. including real-world, widely-used, Python libraries to demonstrate the
utility of our ideas.  Failure determinism directly
produces a more than 5\% improvement in mutation score for an already highly
effective automated test generation tool for a file system, with no
additional specification or test design burden.
